Binary companions of red giant stars in \apogee\ \DR

### 2018-02-27 paper/1-catalog/twoface-catalog.tex
Priors on K v0

\todo{Intro is missing many citations}

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{ r c l }
    \hline
    name & prior & description \\
    \hline
    $P$ & $\ln P \sim \mathcal{U}(1, 32768)~\textrm{day}$ & period \\
    $e$ & $e \sim \textrm{Beta}(0.867, 3.03)$ & eccentricity \\
    $t_0$ & fixed & reference time \\
    $M_0$ & $M_0 \sim \mathcal{U}(0, 2\pi)~\textrm{rad}$ & mean anomaly at reference time \\
    $\omega$ & $\omega \sim \mathcal{U}(0, 2\pi)~\textrm{rad}$ & argument of pericenter \\
    $s^2$ & $\ln s^2 \sim \mathcal{N}(\mu_y, \sigma_y^2)$ & extra variance added to each visit variance \\
    $K$ & TODO & velocity semi-amplitude \\
    $v_0$ & TODO & system barycentric velocity \\
    \hline
    \end{tabular}
    \caption{Summary and description of parameters. $\textrm{Beta}(a, b)$ is the beta distribution with \todo{a, b}, $\mathcal{U}(a, b)$ the uniform distribution over the domain $(a, b)$, and $\mathcal{N}(\mu, \sigma^2)$ is the normal distribution with mean $\mu$ and variance $\sigma^2$.}
    \label{tbl:params}
\end{table}

@@

\subsubsection{``Needs MCMC'': Following up \thejoker\ with MCMC}

>>>>

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{ r c l }
    \hline
    name & prior & description \\
    \hline
    $P$ & $\ln P \sim \mathcal{U}(1, 32768)~\textrm{day}$ & period \\
    $e$ & $e \sim \textrm{Beta}(0.867, 3.03)$ & eccentricity \\
    $t_0$ & fixed & reference time \\
    $M_0$ & $M_0 \sim \mathcal{U}(0, 2\pi)~\textrm{rad}$ & mean anomaly at reference time \\
    $\omega$ & $\omega \sim \mathcal{U}(0, 2\pi)~\textrm{rad}$ & argument of pericenter \\
    $s^2$ & $\ln s^2 \sim \mathcal{N}(\mu_y, \sigma_y^2)$ & extra variance added to each visit variance \\
    $K$ & $\mathcal{N}(0, \sigma_{v}^2)~\kms$ & velocity semi-amplitude \\
    $v_0$ & $\mathcal{N}(0, \sigma_{v}^2)~\kms$ & system barycentric velocity \\
    \hline
    \end{tabular}
    \caption{Summary and description of parameters. $\textrm{Beta}(a, b)$ is the
    beta distribution with shape parameters $(a, b)$, $\mathcal{U}(a, b)$ the
    uniform distribution over the domain $(a, b)$, and $\mathcal{N}(\mu,
    \sigma^2)$ is the normal distribution with mean $\mu$ and variance
    $\sigma^2$.
    For the systemic velocity and semi-amplitude, we use a broad Gaussian prior
    that is formally inconsistent between \thejoker\ and follow-up MCMC sampling
    (see \sectionname~\ref{sec:mcmc}): in \thejoker\ we assume Gaussian priors
    with $\sigma_v$ much larger than the measurement uncertainty so they can be
    neglected ($\sigma_v \approx \infty$), whereas when running MCMC we fix
    $\sigma_v = 10^3~\kms$.}
    \label{tbl:params}
\end{table}

@@

\subsubsection{``Needs MCMC'': Following up \thejoker\ with MCMC}
\label{sec:mcmc}
